Software Ticket Quality

### 2017-11-26 proposal/mprop.tex
Finish discussion on why topics of interest were selected

Secondly, probably the topic of most interest to our research is \emph{issue quality}.
This field is mainly concerned with software tickets and their characteristics: how
important are issue trackers to a software project, what makes for a good bug report,
what impact does bad triaging have etc. While reading multipe

>>>>

Secondly, probably the topic of most interest to our research is \emph{issue quality}.
This field is mainly concerned with software tickets and their characteristics: how
important are issue trackers to a software project, what makes for a good bug report,
what impact does bad triaging have etc. As we are interested in finding out what
features are most important in improving the quality of a ticket, the issue quality
literature I have reviewed proved to be beneficial and provided valuable insight into
how other researchers tried to approach this problem.

The third topic was waste in software projects and how it impacts them. We needed to
look into various communication and tool-related waste in software projects because
having a project with a considerable amount of waste might affect our results and
compromise the evaluation process. We investigated researches that looked into what
are the main types of waste in software projects and how it can be avoided so that
we could apply the findings into selecting the projects.

Last but not least, we did a literature review on sentiment analysis as well because
we will inspect, among other components of a ticket, comments - we want to analyze
the textual representation of comments and see if the overall sentiment might influence
the time it takes to close a ticket (i.e. maybe a negative conversation in comments 
might increase the time it takes to solve the issue).
